---
title: "Yelp_Report"
author: "Rushil Bansal"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
setwd("C:/Users/User/Desktop/EC349/Workings")
source("Yelp Analysis.R")
```

**Github Link:
[github.com/rb048/EC349/tree/main#EC349](github.com/rb048/EC349/tree/main#EC349)**

**Tabula statement**

We're part of an academic community at Warwick.

Whether studying, teaching, or researching, we're all taking part in an
expert conversation which must meet standards of academic integrity.
When we all meet these standards, we can take pride in our own academic
achievements, as individuals and as an academic community.

Academic integrity means committing to honesty in academic work, giving
credit where we've used others' ideas and being proud of our own
achievements.

In submitting my work I confirm that:

1\. I have read the guidance on academic integrity provided in the
Student Handbook and understand the University regulations in relation
to Academic Integrity. I am aware of the potential consequences of
Academic Misconduct.

2\. I declare that the work is all my own, except where I have stated
otherwise.

3\. No substantial part(s) of the work submitted here has also been
submitted by me in other credit bearing assessments courses of study
(other than in certain cases of a resubmission of a piece of work), and
I acknowledge that if this has been done this may lead to an appropriate
sanction.

4\. Where a generative Artificial Intelligence such as ChatGPT has been
used I confirm I have abided by both the University guidance and
specific requirements as set out in the Student Handbook and the
Assessment brief. I have clearly acknowledged the use of any generative
Artificial Intelligence in my submission, my reasoning for using it and
which generative AI (or AIs) I have used. Except where indicated the
work is otherwise entirely my own.

5\. I understand that should this piece of work raise concerns requiring
investigation in relation to any of points above, it is possible that
other work I have submitted for assessment will be checked, even if
marks (provisional or confirmed) have been published.

6\. Where a proof-reader, paid or unpaid was used, I confirm that the
proofreader was made aware of and has complied with the University's
proofreading policy.

7\. I consent that my work may be submitted to Turnitin or other
analytical technology. I understand the use of this service (or
similar), along with other methods of maintaining the integrity of the
academic process, will help the University uphold academic standards and
assessment fairness.

Privacy statement

The data on this form relates to your submission of coursework. The date
and time of your submission, your identity, and the work you have
submitted will be stored. We will only use this data to administer and
record your coursework submission.

Related articles

[Reg. 11 Academic Integrity (from 4 Oct
2021)](https://eur01.safelinks.protection.outlook.com/?url=https%3A%2F%2Fwarwick.ac.uk%2Fservices%2Fgov%2Fcalendar%2Fsection2%2Fregulations%2Facademic_integrity%2F&data=05%7C01%7CRushil.Bansal%40warwick.ac.uk%7C4dd142f8cc154001823908dbf19221e9%7C09bacfbd47ef446592653546f2eaf6bc%7C0%7C0%7C638369382186517743%7CUnknown%7CTWFpbGZsb3d8eyJWIjoiMC4wLjAwMDAiLCJQIjoiV2luMzIiLCJBTiI6Ik1haWwiLCJXVCI6Mn0%3D%7C3000%7C%7C%7C&sdata=7%2FMFmkN5BzSS%2FZ6kSVBKzkAWjQv3PsNvnGZnGhrpirE%3D&reserved=0 "Original URL: https://warwick.ac.uk/services/gov/calendar/section2/regulations/academic_integrity/. Click or tap if you trust this link.")

[Guidance on Regulation
11](https://eur01.safelinks.protection.outlook.com/?url=https%3A%2F%2Fwarwick.ac.uk%2Fservices%2Faro%2Fdar%2Fquality%2Faz%2Facintegrity%2Fframework%2Fguidancereg11%2F&data=05%7C01%7CRushil.Bansal%40warwick.ac.uk%7C4dd142f8cc154001823908dbf19221e9%7C09bacfbd47ef446592653546f2eaf6bc%7C0%7C0%7C638369382186526961%7CUnknown%7CTWFpbGZsb3d8eyJWIjoiMC4wLjAwMDAiLCJQIjoiV2luMzIiLCJBTiI6Ik1haWwiLCJXVCI6Mn0%3D%7C3000%7C%7C%7C&sdata=DksO0dsxi4YBwQ9jUTR2VVJeyhLRPr1DRmBsUfw3olg%3D&reserved=0 "Original URL: https://warwick.ac.uk/services/aro/dar/quality/az/acintegrity/framework/guidancereg11/. Click or tap if you trust this link.")

[Proofreading
Policy](https://eur01.safelinks.protection.outlook.com/?url=https%3A%2F%2Fwarwick.ac.uk%2Fservices%2Faro%2Fdar%2Fquality%2Fcategories%2Fexaminations%2Fpolicies%2Fv_proofreading%2F&data=05%7C01%7CRushil.Bansal%40warwick.ac.uk%7C4dd142f8cc154001823908dbf19221e9%7C09bacfbd47ef446592653546f2eaf6bc%7C0%7C0%7C638369382186533262%7CUnknown%7CTWFpbGZsb3d8eyJWIjoiMC4wLjAwMDAiLCJQIjoiV2luMzIiLCJBTiI6Ik1haWwiLCJXVCI6Mn0%3D%7C3000%7C%7C%7C&sdata=SzJfIs0%2FLo9OYi6jEH66%2Blm78azK3RGV%2BeJM3ApCwII%3D&reserved=0 "Original URL: https://warwick.ac.uk/services/aro/dar/quality/categories/examinations/policies/v_proofreading/. Click or tap if you trust this link.") 

[Education Policy and Quality
Team](https://eur01.safelinks.protection.outlook.com/?url=https%3A%2F%2Fwarwick.ac.uk%2Fservices%2Faro%2Fdar%2Fquality%2Faz%2Facintegrity%2Fframework%2Fguidancereg11%2F&data=05%7C01%7CRushil.Bansal%40warwick.ac.uk%7C4dd142f8cc154001823908dbf19221e9%7C09bacfbd47ef446592653546f2eaf6bc%7C0%7C0%7C638369382186539574%7CUnknown%7CTWFpbGZsb3d8eyJWIjoiMC4wLjAwMDAiLCJQIjoiV2luMzIiLCJBTiI6Ik1haWwiLCJXVCI6Mn0%3D%7C3000%7C%7C%7C&sdata=kNlTWca%2BZw4YQ6h3j1Zaw3qfPD3OuPyTE4MliCQL5%2Bs%3D&reserved=0 "Original URL: https://warwick.ac.uk/services/aro/dar/quality/az/acintegrity/framework/guidancereg11/. Click or tap if you trust this link.")

[Academic Integrity
(warwick.ac.uk)](https://eur01.safelinks.protection.outlook.com/?url=https%3A%2F%2Fwarwick.ac.uk%2Fstudents%2Flearning-experience%2Facademic_integrity&data=05%7C01%7CRushil.Bansal%40warwick.ac.uk%7C4dd142f8cc154001823908dbf19221e9%7C09bacfbd47ef446592653546f2eaf6bc%7C0%7C0%7C638369382186545866%7CUnknown%7CTWFpbGZsb3d8eyJWIjoiMC4wLjAwMDAiLCJQIjoiV2luMzIiLCJBTiI6Ik1haWwiLCJXVCI6Mn0%3D%7C3000%7C%7C%7C&sdata=yOR%2FV3BU9YsN7IyeMqxIojkywTfK2i%2FWrNHc6bOg3wI%3D&reserved=0 "Original URL: https://warwick.ac.uk/students/learning-experience/academic_integrity. Click or tap if you trust this link.")

**I. Business Understanding**

My objectives are to understand the key drivers behind good (and bad)
reviews, and use these findings to train a model to predict the number
of stars given by a user to a business for a specific review. Success
will be evaluated in using root mean square error, and could provide
actionable insights to businesses to boost their visibility and average
ratings on Yelp.

**II. Data Understanding**

There are 5 datasets provided, Reviews, Users, Businesses, Check-ins,
and Tips. Based on the Yelp Documentation, I discarded the Check-ins and
Tips datasets since I could not interpret a causal relationship between
the variables in these data sets and the number of stars given by a
user. Initially, I thought a combination of review text, and average
stars given by the target user and received by the target business would
be the most meaningful.

Simple visualisations of the relationship between key variables such as
review counts for users and for businesses against corresponding average
stars surprisingly yielded some relationship, and average star rating of
each business by the state it operates in also demonstrated meaningful
variance.

```{r}
ggplot(review_data_small, aes(x = stars)) + 
  geom_histogram(bins = 30, col= "white")

ggplot(user_data_small, aes(x=average_stars)) +
  geom_density(kernel="gaussian")

ggplot(business_data, aes(x=stars, y=review_count)) + 
  geom_point()

ggplot(business_data, aes(x = state)) + 
  geom_bar() + scale_y_log10()

ggplot(business_data, aes(x=state,y=stars)) +
  geom_col()

print(business_status_avg)
  
```

**III. Data Preparation**

The bulk of my data preparation was in the form of text analysis. I used
the tf-idf statistic, which is intended to measure how important a word
is to a document in a collection of documents (Silge & Robinson), or in
this case how important a word is to a star rating in a collection of
reviews. After breaking down review texts into one word per row, making
lowercase, removing punctuation, numbers, and common stop words, the
data was still fairly dirty -- with illegible phrases and combinations
of letters with a low n (number of occurrences per star rating). Upon
iterating, I found removing words with less than 20 instances for any
given star rating led to a powerful collection of impactful and
meaningful words when sorted by tf-idf score, such as "crooks" and
"unethical" for 1 star ratings, and "scrumptious" and "delectable" for 5
star ratings.

```{r}
reviews_tfidf %>%
  group_by(stars) %>%
  slice_max(tf_idf, n = 15) %>%
  ungroup() %>%
  ggplot(aes(tf_idf, fct_reorder(word, tf_idf), fill = stars)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~stars, ncol = 3, scales = "free") +
  labs(x = "tf-idf", y = NULL)
```

Following on from this, I used a min-max normalisation to normalise the
tf-idf statistic for each word, and to account for certain words being
part of multiple star ratings, I used an occurrence weighted average to
create scores for each word. Summing the product of these scores with
the number of times the word occurred in the review led to an overall
"sentiment" score for the review, which was one of the variables in my
model.

Upon merging review stars, sentiment score, average stars for users and
businesses, review counts for users and businesses, business open
status, and business state, I had to omit a small number of rows (12
rows) with missing values. I chose to omit these rows instead of
imputing mean values since it was such a small number of instances
compared to the size of the data frame.

**IV. Modelling**

The use of a random forest model came down to the predictive nature of
the task alongside the size and complexity of the datasets. A decision
tree model with such a large set of data would likely result in a high
ρσ^2^ term in the variance, whereas a random forest creates an ensemble
of decision trees, with each one trained on a different subset of the
data and thus reducing variance without significantly increasing bias.
Since we use a random subset of features at each split, trees and
branches are less likely to be identical and the ρ value, or the
correlation between predictions, is close to 0.

**V. Evaluation**

Using 50 trees in my random forest model, my model arrived at an MSE of
0.579, and an accuracy of 57.3%. This error rate is reasonably high and
may be due to three reasons:\
Firstly, the number of trees used is relatively low, due to lack of
computational power.\
Secondly, using only 7 variables is fairly low given the complexity of
the dataset. However, this is primarily to avoid overfitting and
preserve the interpretability ndefinedof the model.\
Thirdly, the sentiment score calculation can be made more accurate
through topical modelling using LDA or other techniques, and also by
using a sentiment lexicon instead of tf-idf statistics.

A feature importance plot below shows that the average stars a user has
given was the most significant predictor in the number of stars a user
gives in a review, as expected intuitively. However, I was surprised
that the remaining features in my model, namely state, business average
stars, my computed sentiment score, user review count, and business
review count were as even in importance as displayed below. I expected
user stars and business stars to be by far the largest predictors.

```{r}
importance_df <- as.data.frame(importance(model))
ggplot(importance_df, aes(x = reorder(row.names(importance_df), MeanDecreaseGini), y = MeanDecreaseGini)) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(x = "Features", y = "Importance", title = "Feature Importance")
```

The confusion matrix below shows the variation in accuracy by star
rating. According to the model, 1 star and 5 star reviews are easiest to
predict and this is expected, since sentiment scores are most
representative for extreme reviews due to aggressive words being used.
Overall, there are not many surprises in the confusion matrix data,
since it reveals a fairly balanced output of predictions vs. actuals.

```{r}
conf_matrix<-confusionMatrix(predictions, test$stars)
conf_matrix_df <- as.data.frame(conf_matrix$table)

ggplot(conf_matrix_df, aes(x = Reference, y = Prediction)) +
    geom_tile(aes(fill = Freq), colour = "white") +  # Heatmap-style tiles
    geom_text(aes(label = sprintf("%0.0f", Freq)), vjust = 1) +  # Add frequencies
    scale_fill_gradient(low = "white", high = "steelblue") +  # Gradient color
    theme_minimal() +
    labs(fill = "Count", x = "Actual Class", y = "Predicted Class", title = "Confusion Matrix")
```

**VI. Biggest Challenge**

My biggest challenge was working in R. I frequently had problems with
cleaning my code which resulted in extraordinary memory usage and
computation time, amplified by a lack of computational power. To combat
this, I have had to use shorthand methods of cleaning unused data-sets
before modelling.

**VII. Data Science Methodology**

I began with the Cross-Industry Standard Process for Data Mining
(CRISP-DM) because I found it very intuitive, and hence allowed me to
structure my natural thoughts in a manner which is the de-facto in the
industry. Throughout the processs, I found that it is structured but
also flexible at the same time, as it has allowed me to iterate many
processes such as data preparation before trying to model, and then
re-preparing data to better fit the model.

**References:**

1.  Grolemund, G. & Wickham, H. 2016. R for Data Science: Import, Tidy,
    Transform Visualise, and Model Data.
2.  Hastie, T.; Tibshirani, R.; Friedman, J. H.; & Friedman, J. H. 2009.
    The Elements of Statistical Learning: Data Mining, Inference, and
    Prediction (Vol. 2). New York: Springer. Ebook and Print Book
    Available at the Warwick Library.
3.  Silge, J. & Robinson, D. 2017. Text Mining with R: A Tidy Approach.
